Genetic Algorithm Based Formula Generation for Curve Fitting in Time Series Forecasting Implemented as Mobile Distributed Computing

### 2019-05-15 Genetic-Algorithm-Based-Formula-Generation-for-Curve-Fitting-in-Time-Series-Forecasting-Implemented-as-Mobile-Distributed-Computing/paper.tex
Pseudo-code was added.

\usepackage{mathptmx}
\usepackage{helvet}
\usepackage{courier}
\usepackage{type1cm}
\usepackage{makeidx}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage[bottom]{footmisc}

@@

@@

Experiments are done as Android mobile application. On the client side Apache Commons Genetic Algorithms Framework \cite{apache01} is used. Mathematical expressions are presented and evaluated with Java build of mXparser \cite{gromada01} software library. On the server side PHP/MySQL based solution \cite{balabanov03} is responsible for synchronization and financial time series data supply.

>>>>

\usepackage{mathptmx}
\usepackage{helvet}
\usepackage{courier}
\usepackage{type1cm}
\usepackage{makeidx}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage[bottom]{footmisc}
\usepackage{listings}
\usepackage{xcolor}
\definecolor{very-light-gray}{gray}{0.95}

@@

\begin{lstlisting}[caption={Genetic algorithm pseudo-code.},label={lst01},backgroundcolor=\color{very-light-gray},frame={single}]
begin
  t = 0;
  initialize P(t);
  evaluate structures in P(t);
  while termination condition not satisfied do
  begin
    t = t + 1;
    select_repro C(t) from P(t-1);
    recombine and mutate structures in C(t)
    forming C’(t);
    evaluate structures in C’(t);
    select_replace P(t) from C’(t) and P(t-1);
  end
end
\end{lstlisting}

@@

Experiments are done as Android mobile application. On the client side Apache Commons Genetic Algorithms Framework \cite{apache01} is used with the parameters listed in Tab. \ref{tab01}. Mathematical expressions are presented and evaluated with Java build of mXparser \cite{gromada01} software library. On the server side PHP/MySQL based solution \cite{balabanov03} is responsible for synchronization and financial time series data supply.

\begin{figure}[b]
\sidecaption
\includegraphics[scale=0.12]{fig01.png}
\caption{EUR/USD rate for two months.}
\label{fig01}
\end{figure}

Publicly available data are used for EUR/USD rate for two months in 2019 year (Fig. \ref{fig01}). Bars in the chart shows the real world price. The line above the bars is the line of the formula generated by the proposed genetic algorithm.

\begin{table}
\caption{Genetic algorithm parameters.}
\label{tab01}
\begin{tabular}{p{6.9cm}p{4.4cm}}
\hline\noalign{\smallskip}
\textbf{Parameter} & \textbf{Value} \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
generation gap & 0.97 \\
crossover rate & 0.95 \\
mutation rate & 0.03 \\
maximum generations & 100 \\
number of individuals & 37 \\
number of variables & floating \\
inserted rate & 100 \% \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
\end{table}

\begin{equation}\label{equ01}
price = 0.485 + 0.01 * sin(day - 2.3) + log(day / 10000)
\end{equation}
